---
title: "p8105_hw5_yl4925"
author: "Yiming Li"
date: "11/14/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 8, 
  fig.asp = 0.8,
  dpi = 200,
  out.width = "90%")
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(ggplot2.continuous.colour = "viridis",
        ggplot2.continuous.fill = "viridis")
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
* Read and describe the raw data
```{r, message=FALSE}
homicide_df = read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, ",", state)) %>%  # create city-state variable
  mutate(whether_solved = case_when(
    disposition == "Closed without arrest" ~ "unsolved",
    disposition == "Open/No arrest" ~ "unsolved",
    disposition == "Closed by arrest" ~ "solved"
  )) %>%  # create a new variable to show whether solved or not
  filter(state != "AL" | city != "Tulsa") # Tulsa should not belong to AL, so remove it
```
Here is a wrong row, where the state of Tulsa is AL not OK. So I remove this row.

* Create unsolved and total homicide dataframe for each state
```{r}
unsolved_VS_total = homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    unsolved_count = sum(whether_solved == "unsolved"),
    total_count = n()
  )
unsolved_VS_total %>% 
  head() %>% 
  knitr::kable()
```

We can easily find solved and unsolved homicide data for specific city such as Baltimore
```{r}
Baltimore_homicide = 
  unsolved_VS_total %>% 
  filter(city_state == "Baltimore,MD") 
```

Then we want to apply proportion test for Baltimore.
```{r}
Baltimore_proportions_test = 
  prop.test(Baltimore_homicide$unsolved_count, sum(Baltimore_homicide$total_count)) %>% 
  broom::tidy()
estimated_proportion = Baltimore_proportions_test %>% 
  pull(estimate)
lower_CI_proportion = Baltimore_proportions_test %>% 
  pull(conf.low)
upper_CI_proportion = Baltimore_proportions_test %>% 
  pull(conf.high)
```
The estimated proportion is `r estimated_proportion`, and the 95% confidence interval for proportion is [`r lower_CI_proportion`, `r upper_CI_proportion`]

* Proportion test for all cities
```{r}
proportion_result = purrr::map2(.x = unsolved_VS_total$unsolved_count, 
                                .y = unsolved_VS_total$total_count, 
                                ~prop.test(x = .x, n = .y)) # use map2 function to do proportion test
tidy_proportion_result = purrr::map(.x = proportion_result, ~broom::tidy(.x)) # use map function to do tidy 

proportion_table = tibble(
  city_state = unsolved_VS_total$city_state, 
  data = tidy_proportion_result
) %>% 
  unnest(cols = data) %>% 
  select(city_state, estimate, conf.low, conf.high) 

proportion_table %>% 
  head() %>% 
  knitr::kable()
```

* Estimate and CI plot
```{r}
proportion_table %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(city_state, estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(title = "City Unsolved Proportion", x = "City,State", y = "Unsolved Proportion")
  
```

# Problem 2
* Get separate file name and path
```{r, message=FALSE}
filename = list.files(path = "./data/p2data")
pathname = str_c("./data/p2data/", filename)
separate_table_list = purrr::map(.x = pathname, ~read_csv(.x)) # use map function to read list element
```

* Integrate dataframe
```{r}
arm_id  = str_remove(filename, pattern = ".csv") #arm and id list
longitudinal_df = tibble(
  arm_id,
  data = separate_table_list
) %>% 
  unnest(cols = data) %>% 
  mutate(arm_and_id = arm_id) %>% 
  separate(arm_and_id, into = c("arm", "id"), sep = "_") 
# we have three variables to show participants status: arm, id, arm_id
longitudinal_df %>% 
  head() %>% 
  knitr::kable()
```

* Do some cleaning 
```{r}
tidy_longitudinal_df = longitudinal_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "time",
    names_prefix = "week_",
    values_to = "observations"
  ) 
```

* Make spaghetti plot
```{r}
tidy_longitudinal_df %>% 
  mutate(time = as.numeric(time)) %>% 
  ggplot(aes(time, observations, color = arm)) +
  geom_line(aes(group = arm_id), alpha = 0.75) +
  geom_smooth(se = FALSE) +
  labs(x = "Time",
       y = "Observation",
       title = "Observation for con and exp")
```

According to smooth line, the observations for con group almost keep the same from week 1 to week 8. But the observations for exp group have the increasing tendency. The overall observations value for exp group is higher than con group.

# Problem 3
* Load iris missing data
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

* Writing filling function
```{r}
fill_missing_iris = function(x) {
  if (is.numeric(x)) {
    value = mean(x, na.rm = TRUE)
    x[is.na(x)] = value
  } else if (is.character(x)) {
    x[is.na(x)] = "virginica"
  }
  return(x)
}
```

```{r}
filled_iris = iris_with_missing %>% 
  map_df(~fill_missing_iris(.x))

filled_iris %>% 
  head() %>% 
  knitr::kable()
```

